Understanding domestic abuse

### 2019-07-23 JeS_fields.tex
Impact summary update

>>>>

Ultimately, the fundamental goal of this research project is to benefit victims of domestic abuse by improving their safety. We aim to do so by working together other stakeholders, including the police, charities, and the government.

Our insights about police mis-recording of domestic abuse will improve the experiences of victims in the CJS, increase trust, and willingness to report future incidents.

victims of domestic abuse more liekly to report and less likely to be seriously harmed, children, police, policymaker - evidence base, charity
